final_project_draft

### 2022-04-25 draft.Rmd
April 25th graded after class commit. Worked on setting up blogdown and connecting to Git. Worked briefly on creating new visualizations.

@@

ggplot(data = country_30, aes(x = order, y = n)) +
  geom_point(colour = "orange") +
  geom_segment(aes(x = order, xend = order, y = 0, yend = n), colour = "blue", linetype = "dotdash") +
  coord_flip() +
  theme_light() +
  theme(axis.ticks.x = element_blank()) +
  labs(x = " ", 
       y = " ",
       title = "How Many Billionaires Are There From the Top 30 Countries?") +
  theme(plot.title = element_text(family = "mono",
                                  size = 20,
                                  face = "bold",
                                   margin = margin(c(t = 40,
                                                    b = 50)),
                                  vjust = 5),
        axis.text = element_text(family = "mono",
                                 face = "bold"),
        axis.title = element_text(family = "mono")) +
  geom_text(aes(label = n, fontface = "bold", family = "mono"), hjust = -0.5, size = 5, colour = "black")
```

## bar plot
```{r}
ggplot(data = country_30, aes(x = order, y = n, fill = n)) +
  geom_col(colour = "black") +
  coord_flip() +
  labs(x = " ", 
       y = " ",
       title = "How Many Billionaires Are There From the Top 30 Countries?",
       fill = "Count") +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 20,
                                   margin = margin(c(t = 40,
                                                    b = 50)),
                                  vjust = 5),
        axis.text = element_text(family = "mono",
                                 face = "bold"),
        axis.title = element_text(family = "mono"),
        legend.title = element_text(family = "mono"),
        legend.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
        legend.position = "none") +
  scale_fill_viridis_b(n.breaks = 6) +
  geom_text(aes(label = n, fontface = "bold", family = "mono"), hjust = -0.5, size = 5, colour = "black")
```

@@

## Continuing to mess around 
```{r}
industry <- billionaires %>% group_by(Industry) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
industry

@@

## Map
```{r}
library(maps)
library(tidyverse)
state_df <- ggplot2::map_data("state")

@@

## New Data Set
```{r}
pvp_dataset <- read_csv("data/pvp_dataset.csv")
pvp_dataset

ggplot(data = pvp_dataset, aes(x = year, y = salary)) +
  geom_line()
pvp_dataset_2 <- read_csv("data/pvp_dataset 2.csv")
pvp_dataset_2
```

>>>>

ggplot(data = countries_10, aes(x = level_order3, y = age)) +
  geom_point(alpha = 0.7, colour = "goldenrod1") +
  coord_flip() +
  geom_point(data = countries_10_average_age, aes(x = Country, y = Average, colour = "Mean Age of Billionaires"),
             size = 4) +
  scale_colour_manual(values = c("Mean Age of Billionaires" = "navy")) +
  labs(x = " ", 
       y = " ",
       title = "Average Age of Billionaires by Country") +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold"),
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 18,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "bold"), 
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic"),
        legend.key.size = unit(1.2, 'cm'),
  legend.box.background = element_rect())
```

@@

ggplot(data = country_30, aes(x = order, y = n, fill = n)) +
  geom_col(colour = "black") +
  coord_flip() +
  labs(x = " ", 
       y = " ",
       title = "How Many Billionaires Are There From the Top 30 Countries?",
       fill = "Count") +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 20,
                                   margin = margin(c(t = 40,
                                                    b = 50)),
                                  vjust = 5),
        axis.text = element_text(family = "mono",
                                 face = "bold"),
        axis.title = element_text(family = "mono"),
        legend.title = element_text(family = "mono"),
        legend.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
        legend.position = "none") +
  scale_fill_viridis_b(n.breaks = 6) +
  geom_text(aes(label = n, fontface = "bold", family = "mono"), hjust = -0.5, size = 5, colour = "black")
```

@@

## Make just one more visualization that makes sense 
```{r}
industry <- billionaires %>% group_by(Industry) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
industry

@@

## Try to make the Map
```{r}
library(maps)
library(tidyverse)
state_df <- ggplot2::map_data("state")

@@

## New Data Set

## Potential questions:

## How has President salary changed over time

## Is there a predominant party or evenly split

## How much more do presidents make compared to vice presidents

## Has salary ever increased from term to term 
```{r}
pvp_dataset <- read_csv("data/pvp_dataset.csv")
pvp_dataset

ggplot(data = pvp_dataset, aes(x = year, y = salary)) +
  geom_line()

pvp_dataset_2 <- read_csv("data/pvp_dataset 2.csv")
pvp_dataset_2

pres_salary <- pvp_dataset_2 %>% filter(position_title == "PRESIDENT OF THE UNITED STATES")
pres_salary

ggplot(data = pres_salary, aes(x = year, y = salary)) +
  geom_line()

ggplot(data = pres_salary, aes(x = year, y = salary, colour = salary)) +
  geom_line()

pres_salary %>% group_by(party) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

ggplot(data = pres_salary, aes(x = salary, y = party)) +
  geom_point()

ggplot(data = pres_salary, aes(x = , y = party, colour = salary)) +
  geom_point()
```
